Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-15 inst/examples/20170201-manuscript.Rmd
ok

```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5, fig.show="hold", out.width="400px"}

for (catal in unique(df00$catalog)) {

@@

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       shape = gatherings,
		       linetype = gatherings))		       
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1,
         aes(color = highlight, fill = highlight))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))
  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Gatherings"),
       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
       	          fill = "none", # guide_legend(title = "Gatherings"),
       	          color = "none" # guide_legend(title = "Gatherings")
		  )
  p <- p + ggtitle(catal)
  print(p)
}
```

@@

```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=14, fig.width=7}
df <- df.full %>% filter(publication_year >= 1640 &
                         publication_year <= 1911) %>%
              group_by(catalog, publication_year) %>%
              summarize(title_length = median(title_length_wordcount),
	      		n = n())

@@

library(gridExtra)
grid.arrange(pics[[1]], pics[[2]], nrow = 2)
```

@@

```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=10}
pics <- list()
for (catalogue in na.omit(unique(df0$catalog))) {

@@

```{r Fig10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
library(dplyr)
catalogue <- "Fennica"
place <- "Vaasa"
minyear <- 1750
maxyear <- 1828

@@

```{r Fig11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
library(dplyr)
place <- "Turku"
catalogue = "Fennica"
df = df0

@@

```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=12}
pics <- list()
theme_set(theme_bw(20))
myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")

>>>>

```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5, fig.show="hold"}
pics <- list()
for (catal in unique(df00$catalog)) {

@@

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       shape = gatherings,
		       linetype = gatherings))		       
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1,
         aes(color = highlight, fill = highlight))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
  p <- p + xlab("Year")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))
  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Gatherings"),
       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
       	          fill = "none", # guide_legend(title = "Gatherings"),
       	          color = "none" # guide_legend(title = "Gatherings")
		  )
  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = ""))
  pics[[catal]] <- p
}
```

```{r Fig3A, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5}
print(pics[[1]])
```

```{r Fig3B, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5}
print(pics[[2]])
```

@@

```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=16}
df <- df.full %>% filter(publication_year >= 1640 &
                         publication_year <= 1911) %>%
              group_by(catalog, publication_year) %>%
              summarize(title_length = median(title_length_wordcount),
	      		n = n())

@@

library(gridExtra)
grid.arrange(pics[[1]], pics[[2]], nrow = 1)
```

@@

```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=16, fig.height=8}
pics <- list()
for (catalogue in na.omit(unique(df0$catalog))) {

@@

```{r Fig10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
library(dplyr)
catalogue <- "Fennica"
place <- "Vaasa"
minyear <- 1750
maxyear <- 1828

@@

```{r Fig11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
library(dplyr)
place <- "Turku"
catalogue = "Fennica"
df = df0

@@

```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=7}
pics <- list()
theme_set(theme_bw(20))
myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
